%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This is the template for submission to HPCA 2018
% The cls file is a modified from  'sig-alternate.cls'
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass{sig-alternate}
\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}


\newcommand{\ignore}[1]{}

%%%%%%%%%
\usepackage[pass]{geometry}
\usepackage{paralist}
\usepackage{pifont}
\usepackage{float}
\usepackage{bm}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{comment}
\usepackage{cases}
\usepackage{bbm}
\usepackage{graphicx}
\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{algpseudocode}
%\usepackage{csvsimple}
\usepackage{array}
%\usepackage{flushend}
\usepackage{balance}
\usepackage{multirow}
\usepackage{mathptmx} % This is Times font
\usepackage{mathtools}
%\newcommand{\ignore}[1]{}
\usepackage[normalem]{ulem}
\usepackage[hyphens]{url}
\usepackage{fancyhdr}
\usepackage{enumitem}
\usepackage{nicefrac}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{subfloat}
\usepackage{graphics}
\usepackage{verbatim}
%\usepackage{subfig}
\usepackage{color}
\usepackage{footnote}
%newadded for url
\usepackage{url}
%\usepackage{hyperref}
\usepackage[bookmarks=false]{hyperref}
%%%%for mod%%%%
%\usepackage{intcalc}
%\usepackage{adjustbox}
%\usepackage{scrextend}
%%%%%%%%%

\setlist[itemize]{leftmargin=0.2in}
\setlist[enumerate]{leftmargin=0.2in}


\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}{Proposition}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{corollary}{Corollary}[section]
\newtheorem{claim}{Claim}[section]
\newtheorem{definition}{Definition}

%\newtheorem{definition}{Definition}%[section]
\newtheorem{example}{Example}%[section]
\newtheorem{conjecture}{Conjecture}%[section]
\newtheorem{construction}{Construction}%[section]
\newtheorem{remark}{Remark}%[section]

%\newtheorem{remark}{Remark}%[section]
\newtheorem{case}{Case}%[section]
\newtheorem{assumption}{Assumption}

%%%%%%%%%%%---SETME-----%%%%%%%%%%%%%
\newcommand{\hpcasubmissionnumber}{376}
\newcommand*\cn{{\color{red}{\textbf{[Citation Needed]}}}}
\newcommand*\Ankit[1]{{\color{red}{\textbf{[ANKIT:~#1]}}}}
\newcommand*\Hardik[1]{{\color{blue}{\textbf{[HARDIK:~#1]}}}}
\newcommand*\Ethan[1]{{\color{magenta}{\textbf{[ETHAN:~#1]}}}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\fancypagestyle{firstpage}{
  \fancyhf{}
\setlength{\headheight}{50pt}
\renewcommand{\headrulewidth}{0pt}
  \fancyhead[C]{\normalsize{HPCA 2018 Submission
      \textbf{\#\hpcasubmissionnumber} -- Confidential Draft -- Do NOT Distribute!!}}
  \pagenumbering{arabic}
}

%%%%%%%%%%%---SETME-----%%%%%%%%%%%%%
\title{Coded Access Architectures for Dense Memory Systems} 
\author{}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\maketitle
\thispagestyle{firstpage}
\pagestyle{plain}

\input{tex_files/00abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Intrroduction
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{tex_files/01introduction.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Background and Related Work
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{tex_files/02background.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Code design
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{tex_files/03codeDforDM.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Coding Architecture for HBM
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{tex_files/04codingArchitecture.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Experiment methodology
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{tex_files/05experimentMethod.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Results
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{tex_files/results.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Conclusion
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{tex_files/conclusion.tex}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Appendices
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\input{tex_files/conclusion.tex}
\section{HBM details: removed from background sections}

Each HBM channel is expected to provide a 128-bit data interface that supports up to 1-2 Gbps of data rate per signal equivalent to 500-1000MHz of DDR memory. This is equivalent to 16-32 GB/sec of bandwidth per channel. With 8 channels stacked together it can provide 128-256 GB/sec of access bandwidth per stack. 

The HBM specification document lists two modes of operation: legacy mode and pseudo channel mode. A memory controller can support either the legacy or the pseudo channel mode. 

In case of the legacy mode, each read or write transaction transfers 256 bits in a burst that consists of 2 cycles of 128 bits each. In pseudo channel mode, the 128-bit bus is split into 2 individual 64-bit segments. On each segment, a read or write transaction transfers 256 bits as well, but in a burst that lasts 4 cycles (of 64 bits each). The pseudo channel conceptually divides the memory of a single channel in half and assigns each half to a fixed pseudo channel. The pseudo channels share the same address and command bus: you can send a command and addresses to one pseudo channel or the other, but not to both.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Acknowledgements
%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Acknowledgements}
This document is derived from previous conferences, in particular HPCA 2017.  We thank Daniel A. Jimenez,  Elvira Teran for their inputs.

%%%%%%% -- PAPER CONTENT ENDS -- %%%%%%%%

%\newpage 

%%%%%%%%% -- BIB STYLE AND FILE -- %%%%%%%%
\bibliographystyle{ieeetr}
\bibliography{tex_files/ref}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}
