\section{Conclusion}
\label{sec:conclusion}
%\Ethan{Duplicate of abstract?}
This paper proposes a coded memory system that is amenable to multi-bank DRAM architectures such as HBM. Our Reed-Solomon based coding scheme reduces bank conflicts by creating many redundant ways to access a requested data element. This is achieved by assigning some banks to be dedicated parity banks. A memory controller then decides which frequently-used data elements should be stored in these parity banks. Simulations on the PARSEC benchmarks show significant reduction in CPU latency when the controller's reorder buffer is of sufficient length. Our detailed experimental results demonstrate the utility of our memory controller design for improving the performance of uncoded memory systems.

The parity banks in our proposed memory system improve the system's performance in several scenarios. The inclusion of parity banks brings additional memory overhead to the system. One potential method for minimizing this memory overhead is dynamic coding techniques which produce {\em shallow} parity banks. In dynamic coding, heavily accessed regions of memory are identified and selectively encoded into parity banks. Thus, small {\em shallow} parity banks are generated which can serve requests for the most heavily accessed regions of memory, and the inclusion of these shallow banks incur only a small memory overhead.

%In this paper, we explore the use of coding theory in DDR and high bandwidth memory (HBM) system. Conventional DDR systems use timing optimization techniques around DDR protocol to improve the efficiency of accesses. In this work we propose increasing redundancy to help distribute access across DRAM pages. This will help in efficient retrieval of data. These schemes will be evaluated and optimized with several iterations. The aim is to find the best performing code design scheme given the performance requirement compared to alternatives. Our proposed scheme results in a decrease in the number of contended memory accesses between cores, therefore reducing the overall latency of the system. The reduction in the latency can be seen directly as an increase in the overall system performance. We show that with a memory overhead of  $15$\%, we can enable $4$ extra accesses to a bank while remaining within the given design parameters. We also included emphasis on the code design and optimization of the access scheduler and made significant process in improving the design emulation on the Ramulator platform.
%
%This paper explores the use of coding theory in double data rate (DDR) and high bandwidth memory (HBM) systems. Conventional DDR systems use timing optimization techniques around the DDR protocol to improve access efficiency. This paper proposes utilization of coding techniques to store data across DRAM pages in a redundant manner. The introduced redundancy creates multiple alternatives to access a particular data element stored in the DRAM; consequently making the data retrieval more efficient. This paper proposes a memory design which is based on Reed Solomon codes. The proposed design decreases the number of contended memory accesses between cores. This helps reduce the overall latency of the system, leading to increased performance. Various benchmarking experiments carried out on the proposed design show that the designed memories can enable $4$ extra accesses to a bank while incurring a storage overhead of only $15$\% and remaining within the acceptable values of other design parameters. 

\input{tex_files/prefetching.tex}